Testing perceptual accuracy in a U.S. general population survey using stacked bar charts

### 2023-12-21 SDSS-2023/testing-charts-accuracy.tex
adding section numbers

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

@@

\hypertarget{study-design-stimulus}{%
\subsection{Study design -- stimulus}\label{study-design-stimulus}}

@@

\hypertarget{question-text}{%
\paragraph{Question text}\label{question-text}}

@@

\hypertarget{alignment}{%
\paragraph{Alignment}\label{alignment}}

@@

\hypertarget{study-design-participants}{%
\subsection{Study design --
participants}\label{study-design-participants}}

@@

\hypertarget{study-design-survey-weighting}{%
\subsection{Study design -- survey
weighting}\label{study-design-survey-weighting}}

@@

\hypertarget{respondents}{%
\subsubsection{Respondents}\label{respondents}}

@@

\hypertarget{accuracy-of-responses}{%
\subsubsection{Accuracy of responses}\label{accuracy-of-responses}}

@@

\hypertarget{respondent-behavior}{%
\subsubsection{Respondent behavior}\label{respondent-behavior}}

@@

\hypertarget{differences-across-demographic-groups}{%
\subsubsection{Differences across demographic
groups}\label{differences-across-demographic-groups}}

>>>>

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{study-design}{%
\section{Study design}\label{study-design}}

\hypertarget{study-design-stimulus}{%
\subsection{Stimulus}\label{study-design-stimulus}}

@@

\hypertarget{question-text}{%
\subsubsection{Question text}\label{question-text}}

@@

\hypertarget{alignment}{%
\subsubsection{Alignment}\label{alignment}}

@@

\hypertarget{study-design-participants}{%
\subsection{Participants}\label{study-design-participants}}

@@

\hypertarget{study-design-survey-weighting}{%
\subsection{Survey
weighting}\label{study-design-survey-weighting}}

@@

\hypertarget{respondents}{%
\subsection{Respondents}\label{respondents}}

@@

\hypertarget{accuracy-of-responses}{%
\subsection{Accuracy of responses}\label{accuracy-of-responses}}

@@

\hypertarget{respondent-behavior}{%
\subsection{Respondent behavior}\label{respondent-behavior}}

@@

\hypertarget{differences-across-demographic-groups}{%
\subsection{Differences across demographic
groups}\label{differences-across-demographic-groups}}
